Notas Historicas

### 2018-01-18 man/notes/notes_drought.Rmd
move notes to new folder

---
title: "notes Drought"
author: "AJ Perez-Luque (@ajpelu)"
date: "2016 Aug"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../references.bib
csl: ../ecology.csl
---

>>>>

---
title: "notes Drought"
author: "AJ Perez-Luque (@ajpelu)"
date: "2016 Aug"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

### 2018-01-18 man/notes/notes_history.Rmd
move notes to new folder

---
title: "Notas Historicas"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../references.bib
csl: ../ecology.csl
---

>>>>

---
title: "Notas Historicas"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---
